An Improved Approximate-Bayesian Model-choice Method for Estimating Shared Evolutionary History

### 2014-02-19 manuscripts/dpp-msbayes/dpp-msbayes-main.tex
Using `\url` for all URLs in manuscript.

\subsection{The model}
In this section, we describe our model, which is a modification of the model
implemented in \msb \citep{Huang2011,Oaks2012}.
The code implementing the new model is freely available in the open-source
software package \dppmsbayes
(\href{https://github.com/joaks1/dpp-msbayes}{https://github.com/joaks1/dpp-msbayes}).
Our analyses described below utilize the freely avaliable, open-source software
package \pymsbayes (\href{https://github.com/joaks1/PyMsBayes}{https://github.com/joaks1/PyMsBayes}),
which is a Python API that provides a multi-processing interface to \msb and
\dppmsbayes.
We performed the work described below following the principles of
Open Notebook Science.
Using version-control software, we make progress in all aspects of the work
freely and publicly available in real-time at
\href{https://github.com/joaks1/msbayes-experiments}{https://github.com/joaks1/msbayes-experiments}.
All information necessary to reproduce our results is provided there.
We follow much of the notation of \citet{Oaks2012}, but modify it to
aid in our description of the new model.
A summary of our notation can be found in Table \ref{tabNotation}.

>>>>

\subsection{The model}
In this section, we describe our model, which is a modification of the model
implemented in \msb \citep{Huang2011,Oaks2012}.
The code implementing the new model is freely available in the open-source
software package \dppmsbayes
(\href{https://github.com/joaks1/dpp-msbayes}{\url{https://github.com/joaks1/dpp-msbayes}}).
Our analyses described below utilize the freely avaliable, open-source software
package \pymsbayes (\href{https://github.com/joaks1/PyMsBayes}{\url{https://github.com/joaks1/PyMsBayes}}),
which is a Python API that provides a multi-processing interface to \msb and
\dppmsbayes.
We performed the work described below following the principles of
Open Notebook Science.
Using version-control software, we make progress in all aspects of the work
freely and publicly available in real-time at
\href{https://github.com/joaks1/msbayes-experiments}{\url{https://github.com/joaks1/msbayes-experiments}}.
All information necessary to reproduce our results is provided there.
We follow much of the notation of \citet{Oaks2012}, but modify it to
aid in our description of the new model.
A summary of our notation can be found in Table \ref{tabNotation}.
